Supplemental material

### 2024-04-23 paper/resp_referee.qmd
update arima + paper

> 3. Section 1.2.1: these results are well-known; the derivatives of the frequency response function 
> at $\omega = 0$ yield the conditions. So the results could be stated with references, and the 
> derivations omitted, and this subsection compactified.

@@

The $\forall q$ was omitted and this section was rewritten to make it clearer.

@@

> 9. Page 15, line 40: I couldn't find the matrix $T$ defined. How is it connected to timeliness? 
> That is, when you display the entries of the matrix $T$, you need to make a connection between 
> those values and the concept of timeliness.

@@

> 12. Appendix B: rather than typing out the R code, it would be better to have the files available 
> as supplementary material. (Or possibly put in a github repo and provide the links in the 
> text.)

@@

> 1. The authors should provide a clear definition of trend-cycle, $TC_t$, and irregular, $I_t$. In other words, how is the decomposition $y_t =TC_t+I_t$ identified?
> In section 1 they seem to hint at the interpretation of $TC_t$ as the low-pass component of yt with cutoff frequency $\pi/6$ (and correspondingly they interpret $I_t$ as the high-pass component). 
> This point should be clarified, I think. 
> Related questions are: are $y_t$ and its components stochastic or deterministic? 
> The treatment in section 1.2.1 suggests that $TC_t$ is an unknown possibly nonlinear deterministic function of time. 
> The variance inflation factor $\sum_k \theta_k^2$ implies that $I_t$ is white noise.

@@

@@

*It was added in the beginning of section 3 and 4 than the bandwidth is fixed. Nearest neighbour bandwidth was added in supplemental material.*

@@

@@

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.  It may be worth considering (in addition) shorter series.  Another thought is that the ARIMA model being used to extend the series appears to be modeled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?

@@

@@

@@

1) The paper lacks in describing the contribution from the beginning. 
I had to read the paper a couple of times to clearly identify the contribution.
I found the contribution of the paper clearly stated on page 16, but I think I should come before in the text.

2) The paper omits to consider the Covid19 period and how this influences the trend and cycle decomposition. 
I understand that this is not the main focus of the paper, but at least the authors should address this problem in word and possible solution to address it, e.g. outlier correction, robust distributions, etc.

>>>>

> 3. Section 1.2.1: these results are well-known; the derivatives of the frequency response function at $\omega = 0$ yield the conditions. 
So the results could be stated with references, and the derivations omitted, and this subsection compactified.

@@

*The $\forall q$ was omitted and this section was rewritten to make it clearer.*

@@

> 9. Page 15, line 40: I couldn't find the matrix $T$ defined. How is it connected to timeliness? 
That is, when you display the entries of the matrix $T$, you need to make a connection between those values and the concept of timeliness.

@@

> 12. Appendix B: rather than typing out the R code, it would be better to have the files available as supplementary material. 
(Or possibly put in a github repo and provide the links in the text.)

@@

> 1. The authors should provide a clear definition of trend-cycle, $TC_t$, and irregular, $I_t$. In other words, how is the decomposition $y_t =TC_t+I_t$ identified?
> In section 1 they seem to hint at the interpretation of $TC_t$ as the low-pass component of $y_t$ with cutoff frequency $\pi/6$ (and correspondingly they interpret $I_t$ as the high-pass component). 
> This point should be clarified, I think. 
> Related questions are: are $y_t$ and its components stochastic or deterministic? 
> The treatment in section 1.2.1 suggests that $TC_t$ is an unknown possibly nonlinear deterministic function of time.
> The variance inflation factor $\sum_k \theta_k^2$ implies that $I_t$ is white noise.

The modelled of the input time series is now describe more precisely in section 2 (previous section 1). $TC_t$ is here considered as deterministic

@@

*Since section 1.3.2 was removed (not central to the paper and simplify the reading), the section 1.2.2 and the reference to the minimization of the noise component (through the minimisation of the variance is it is modelled as a white noise) is removed*

@@

*It was added in the beginning of new sections 3 and 4 than the bandwidth is fixed. Nearest neighbour bandwidth was added in supplemental material but it doesn't improve the results in therm of phase shift. I can be explain that the bi*

@@

In local polynomial smoothing, the notion of bias is associated to the approximation error of the smoothed series by a polynomial degree of order $d$.
It can thus be writer as

@@

*A lecture note is added*

@@

> The author simulates time series of length 60 years to illustrate the methodology at the end of the series.
It may be worth considering (in addition) shorter series. 
Another thought is that the ARIMA model being used to extend the series appears to be modeled using the full series; what if the ARIMA model used to extend the series was instead estimated using just a short span toward the end of the series?
*Indeed it is in general not relevant to identify an ARIMA model on a monthly time series of length 60 years.*
In our case, since the same data generation process remains the same, it could be relevant and leads to better results in terms of delay to detect turning points (in supplement materials, a plot is added comparing the results with different spans to identify/estimate the ARIMA model).
However, on the main text, we now only used 12 years to identify the ARIMA model, to be closer to what would be done on real series.

@@

*Bibliography added and the R icon was removed*

@@

*A lecture note is added in the tables and more explainations are added to the text*

@@

> 1) The paper lacks in describing the contribution from the beginning. 
I had to read the paper a couple of times to clearly identify the contribution.
I found the contribution of the paper clearly stated on page 16, but I think I should come before in the text.

> 2) The paper omits to consider the Covid19 period and how this influences the trend and cycle decomposition. 
I understand that this is not the main focus of the paper, but at least the authors should address this problem in word and possible solution to address it, e.g. outlier correction, robust distributions, etc.

### 2024-04-23 paper/supp_material.qmd
update arima + paper

# Quarterly data

@@

# Nearest neighbour bandwidth

@@

>>>>

#

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_local_final_lc.pdf")
```

Distribution of phase shifts associated to the local parametrisation of the linear-constant (LC) filter using the final estimates of $\delta/\sigma$ in function of the length of the henderson filter used to estimate $\sigma$ ($h$) and the degree of the trend to estimate $\delta$ ($d$)/
:::

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_local_lc.pdf")
```

Distribution of phase shifts associated to the local parametrisation of the linear-constant (LC) filter using real time estimates of $\delta/\sigma$ in function of the length of the henderson filter used to estimate $\sigma$ ($h$) and the degree of the trend to estimate $\delta$ ($d$)/
:::

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_local_ql.pdf")
```

Distribution of phase shifts associated to the local parametrisation of the quadratic-linear (QL) filter using real time estimates of $\delta/\sigma$ in function of the length of the henderson filter used to estimate $\sigma$ ($h$) and the degree of the trend to estimate $\delta$ ($d$)/
:::

\newpage
# Quarterly data

@@

\newpage
# Nearest neighbour bandwidth

@@

::: {#fig-graphs-impact-span}
```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("img/simulations/phase_shift_simul_nn_lp.pdf")
```
Note:
